---
title: "skinny_questions"
output: html_document
---

```{r}
rm(list = ls())

library(dplyr)
library(stringr)
library(lubridate)
library(readr)

# 1. Read the CSV
claire_skinny_dorsals_in_ <- read_csv("data/claire_skinny_dorsals(in).csv")

# 2. Clean and subset
df_subset <- claire_skinny_dorsals_in_ %>%
  # Make the column names easier to use
  rename(
    Keyword_export = `Keyword-export`,
    Date_Time      = `Date Time`
  ) %>%
  # Make sure the key columns are plain character before using them
  mutate(
    Keyword_export = as.character(Keyword_export),
    Date_Time      = as.character(Date_Time)
  ) %>%
  # Derive Sex, Age, and parse Date_Time
  mutate(
    Sex = dplyr::case_when(
      str_detect(Keyword_export, "Male")    ~ "Male",
      str_detect(Keyword_export, "FemaleJ") ~ "FemaleJ",
      TRUE                                  ~ NA_character_
    ),
    Age = dplyr::case_when(
      str_detect(Keyword_export, regex("juv/calf", ignore_case = TRUE)) ~ "Juvenile/Calf",
      str_detect(Keyword_export, regex("juv",      ignore_case = TRUE)) ~ "Juvenile",
      str_detect(Keyword_export, regex("calf",     ignore_case = TRUE)) ~ "Calf",
      TRUE                                                              ~ "Adult"
    ),
    Date_Time = mdy_hm(Date_Time, quiet = TRUE)
  ) %>%
  select(Title, Sex, Age, Date_Time)

# Quick check
head(df_subset)

```

```{r}
library(dplyr)
library(stringr)
library(lubridate)
library(readr)

df <- read_csv("data/claire_skinny_dorsals(in).csv",
               show_col_types = FALSE) %>%
  rename(
    Keyword_export = `Keyword-export`,
    Date_Time      = `Date Time`
  )


# Per-photo data with Skinny flag
df_subset <- df %>%
  mutate(
    Sex = case_when(
      str_detect(Keyword_export, "Male")    ~ "Male",
      str_detect(Keyword_export, "FemaleJ") ~ "FemaleJ",
      TRUE                                  ~ NA_character_
    ),
    Age = case_when(
      str_detect(Keyword_export,
                 regex("juv\\s*/\\s*calf|jut\\s*/\\s*calf",
                       ignore_case = TRUE)) ~ "Juvenile/Calf",
      str_detect(Keyword_export,
                 regex("calf", ignore_case = TRUE)) ~ "Calf",
      str_detect(Keyword_export,
                 regex("juv",  ignore_case = TRUE)) ~ "Juvenile",
      TRUE ~ "Adult"
    ),
    Skinny = if_else(
      str_detect(Keyword_export,
                 regex("claire_skinny", ignore_case = TRUE)),
      "Yes", "No"
    ),
    Date_Time = as.Date(mdy_hm(Date_Time, quiet = TRUE)),
    Date      = Date_Time
  ) %>%
  select(Title, Sex, Age, Skinny, Date_Time, Date)

# One row per whale per day
df_daily <- df_subset %>%
  group_by(Title, Date) %>%
  summarise(
    Sex    = first(na.omit(Sex), default = NA_character_),
    Age    = first(na.omit(Age), default = NA_character_),
    Skinny = if_else(any(Skinny == "Yes", na.rm = TRUE),
                     "Yes", "No"),
    .groups = "drop"
  ) %>%
  transmute(Title, Sex, Age, Skinny, Date_Time = Date)

head(df_daily)

write.csv(df_daily, "df_daily_cleaned.csv", row.names = FALSE)


```


add year column
```{r}
library(lubridate)

df_daily <- df_daily %>%
  dplyr::mutate(Year = year(Date_Time))

write.csv(df_daily, "df_daily.csv", row.names = FALSE)

```


```{r}
table(df_daily$Skinny)

str(df_daily$Sex)
df_daily$Sex <- factor(df_daily$Sex)

table(df_daily$Sex, df_daily$Skinny)


```

bodyCondition ~ sex + (1|Year)
```{r}
library(lme4)

# Convert Skinny to a binary factor (1 = Yes, 0 = No)
df_daily$Skinny <- ifelse(df_daily$Skinny == "Yes", 1, 0)

mod1 <- glmer(Skinny ~ Sex + (1 | Year),
              data = df_daily,
              family = binomial)
summary(mod1)




```

in the above output suggests there are some variability among years-some years likely have more skinny individuals than others

checked to make sure every year in teh y axis was accounted for in the df dataset-it is, however there are a couple of years with not many whales-a mistake maybe? 2009 2008 1991 1988

The red lines indicate a lower than average probability of whales being detected as skinny
Blue lines indicate higher than average probability of whales being detected as skinny

```{r}
ranef(mod1)$Year

#install.packages("sjPlot")
library(sjPlot)
plot_model(mod1, type = "re", sort.est = TRUE)

```

trying to fit the effect as a GAM
-unsure if i did it right or what im looking for?
```{r}
library(mgcv)

gam_year <- gam(Skinny ~ s(Year, k = 5),
                data   = df_daily,
                family = binomial,
                method = "REML")
summary(gam_year)
plot(gam_year, pages = 1)


```


skinnyness as an indicator of health--> if skinny is it the last year seen?-->modelling dissapearance
```{r}
rm(list = ls())

library(dplyr)
library(stringr)
library(lubridate)
library(readr)

# 1. Read the original Lightroom export
df <- read_csv("data/claire_skinny_dorsals(in).csv",
               show_col_types = FALSE) %>%
  rename(
    Keyword_export = `Keyword-export`,
    Date_Time      = `Date Time`
  )

# 2. Add Skinny flag and Year column
df2 <- df %>%
  mutate(
    Skinny = str_detect(Keyword_export, regex("skinny", ignore_case = TRUE)),
    Date_Time = mdy_hm(Date_Time, quiet = TRUE),
    Year = year(Date_Time)
  )

# 3. Table of all whales that were skinny & the year(s) they were skinny
skinny_whales <- df2 %>%
  filter(Skinny) %>%
  distinct(Title, Year)

# 4. Table of each whale's LAST year seen (from the full dataset)
last_year_seen <- df2 %>%
  group_by(Title) %>%
  summarise(last_year_seen = max(Year, na.rm = TRUE), .groups = "drop")

# 5. Add the last-year-seen info to the skinny whale table
skinny_with_last <- skinny_whales %>%
  left_join(last_year_seen, by = "Title") %>%
  arrange(Title, Year)

# 6. View results
View(skinny_with_last)

write_csv(skinny_with_last, "skinny_whales_with_last_year.csv")


```

count where year == year_last_seen

also calculate proportion of whales who dissapear from catalogue while skinny
```{r}
sum(skinny_with_last$Year == skinny_with_last$last_year_seen, na.rm = TRUE)

mean(skinny_with_last$Year == skinny_with_last$last_year_seen)


```



average number of social partners of skinny whales
-each whale counted once per year
-doubles possible-consider that whales may recover 
```{r}
library(dplyr)

skinny_social <- merged_df %>%
  group_by(Title, Year) %>%
  summarise(
    # was this whale ever labelled skinny in this year?
    Skinny_year = any(Skinny == "Yes", na.rm = TRUE),

    # social metrics (constant within Title–Year, so just take first)
    Degree   = first(Degree),
    Strength = first(Strength),
    .groups = "drop"
  )

avg_social_skinny <- skinny_social %>%
  filter(Skinny_year) %>%
  summarise(
    n_whale_years = n(),
    mean_degree   = mean(Degree,   na.rm = TRUE),
    sd_degree     = sd(Degree,     na.rm = TRUE),
    mean_strength = mean(Strength, na.rm = TRUE)
  )

avg_social_skinny

avg_social_nonskinny <- skinny_social %>%
  filter(!Skinny_year) %>%
  summarise(
    n_whale_years = n(),
    mean_degree   = mean(Degree,   na.rm = TRUE),
    sd_degree     = sd(Degree,     na.rm = TRUE),
    mean_strength = mean(Strength, na.rm = TRUE)
  )

avg_social_nonskinny


```





maybe use associated_entries from NBW to determine group size?

